---
title: "SNRBoost"
output: 
  bookdown::html_vignette2:
    toc: true
    highlight: tango
    number_sections: false
vignette: >
  %\VignetteIndexEntry{SNRBoost}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",     
  dev = "jpeg", dpi=300, out.width = "80%", 
  fig.height = 9, fig.width = 9,
  fig.align='center', fig.pos="h!")
```

```{r setup}
library(SNRBoost)
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(tidyverse)
require(viridis)
col_qual <- RColorBrewer::brewer.pal(n=3, name="Dark2")
```

# Data Generation

Two data generation model to test the merging methods: 
- Gaussian white nosie 
- sinewave 

```{r dat, fig.height=7, fig.width=9}
# Random seed
set.seed(20240924)

### Step 1: Data parameters
p <- 3 # number of datasets
n <- 300 # data length

ecc <- 0.3 # error cross-correlation [0,1]
SNRdB <- 0.1 # SNR in dB

model <- switch(2,"rand","sine")

### Step 2: Synthetic data generation
# Signal and error: y and e
n_ensemble <- 100
df_mat <- vector('list', n_ensemble)
for(i_r in 1:n_ensemble){
  ######## scaling factor (a)##########
  #a <- matrix(rep(1, p), ncol=1)  # 1-vector
  a <- matrix(runif(p), ncol=1) # non-1-vector (for test)
  
  generated_data <- dataGEN(n, p, ecc, SNRdB, model=model)
  y <- generated_data$y %>% matrix(ncol=1)
  e <- generated_data$e
  
  # Observation: x = a*signal + error
  x <- y %*% t(a) + e
  
  # Signal power and covariance matrices of e and x
  Ey2 <- var(y[,1]); sum(y^2)/(n-1)
  #Ey2 <- sum(y^2)/(n)
  EeeT <- cov(e)
  ExxT <- cov(x)
  N <- EeeT / Ey2 # error-to-signal ratio
  N

  
  df_mat[[i_r]]$y <- y
  df_mat[[i_r]]$x <- x
  df_mat[[i_r]]$e <- e
  df_mat[[i_r]]$N <- N
  df_mat[[i_r]]$a <- a
}

plot.ts(cbind(y,x))
```

## Statistics of raw dataset

```{r stat}
# MSE of observations
MSE_ori <- sapply(1:p, function(i) mean((y-x[,i])^2))

# Pearson correlation of observations
R2_ori <- cor(y,x)

# Printing metrics
cat("+ Metrics for original data\n")
cat(" * MSE for x:", round(MSE_ori, 3), "\n")
cat(" * R2 for x:", round(R2_ori, 3), "\n")
```

## Data overview

```{r fig}
spc.method <- switch(2, "pgram", "ar")
spc.kernel <- kernel("fejer", 100, r=6)

spectrum_df <- function(data, span=2, log="no", kernel=spc.kernel, method=spc.method) {
  spec <- spectrum(data, span=span, log=log, kernel=kernel, method=method, plot=F)
  
  # Create a dataframe with frequency and spectral density
  delta<- 1 # sampling interval = time sequence
  spec_df <- data.frame(Frequency = spec$freq/delta, SpectralDensity = 2*spec$spec)
  
  return(spec_df)
}

df_raw <- data.frame(No=1:n, x, y) %>% gather(Group, value, 2:5)
summary(df_raw)

my_labeller <- as_labeller(c(X1="x[1]",
                             X2="x[2]",
                             X3="x[3]",
                             y="y [Truth]"), 
							 default = label_parsed)

df_raw$Group <- factor(df_raw$Group, levels = c("y","X1","X2", "X3"))


fig <- ggplot(df_raw) + 
  geom_line(aes(x=No, y=value, color=Group),linewidth=0.5) + 

  facet_wrap(Group~., strip.position="left", ncol = 1, labeller = my_labeller) + 
  
  scale_color_manual(values=c("black", col_qual)) + 
  labs(x=NULL, y=NULL) + 
  
  theme_bw() +
  theme(text = element_text(size = 20, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.1,0.1, 0.1), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_blank(), 
        
        panel.spacing = unit(0, "lines"), 
        strip.background = element_blank(), 
        strip.text.y.left = element_text(angle = 0), 

        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 

        legend.position = "none",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm"))

fig

```

# WA and SNR optimaztion

```{r snr}
## Merging using true parameters
ue <- rep(1/p, p)  # equal weight
uw <- WA(EeeT) # weighted average
us <- SNRopt(N, a) # SNR-opt

y_eq <- x %*% ue
y_wa <- x %*% uw
y_snr <- x%*%us

plot.ts(cbind(y,y_wa,y_snr))

cor(y,cbind(y_wa, y_snr))

```

## Merged products in time domain

```{r merge1}

df_y <- data.frame(No=1:n, y, y_eq,y_wa,y_snr) %>% gather(Group, value,2:5)
summary(df_y)

my_labeller <- as_labeller(c(y="y [Truth]", 
                             y_eq="y [Equal]", 
                             y_wa="y [WA]",
                             y_snr="y [SNR]"), 
							 default = label_parsed)

df_y$Group <- factor(df_y$Group, levels = c("y","y_eq","y_wa", "y_snr"))
fig1.c <- ggplot(df_y %>% subset(Group!="y")) + 
  geom_line(aes(x=No, y=value, color=Group), linewidth=0.5) + 

  facet_wrap(Group~., strip.position="left", ncol = 1, scale="fixed", labeller = my_labeller) + 
  labs(x=NULL, y=NULL) + 
  #scale_color_manual(values=col_qual) + 
  scale_color_manual(values=c("red","blue","green")) + 
  
  theme_bw() +
  theme(text = element_text(size = 20, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.1,0.1, 0.1), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_blank(), 
        
        panel.spacing = unit(0, "lines"), 
        strip.placement = "outside", 
        strip.background = element_blank(), 
        strip.text.y.left = element_text(angle = 0), 

        #axis.title.x = element_text(angle = 0), 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),

        legend.position = "none",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm"))

fig1.c

```

## Spectram analysis - X

```{r fig1-x}
y_spec <- spectrum_df(y)
x_spec <- sapply(1:p, function(i) spectrum_df(x[,i], span=1)$Spec)

df_spec <- data.frame(Freq=y_spec$Frequency, 
                        y=y_spec$SpectralDensity, 
                        x_spec) %>% 
  gather(Group,Spec,2:5)

df_spec$Group <- factor(df_spec$Group, levels = c("y","X1","X2", "X3"))

summary(df_spec)

fig1 <- ggplot(df_spec) +

  geom_line(aes(Freq, Spec, color=Group),linewidth=1) +

  scale_y_log10("Spectrum", limits=c(10e-5,10e3),
                breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +

  scale_color_manual(values=c("black",col_qual), labels=expression(y[Truth],x[1],x[2],x[3])) + 
  labs(x="Frequency", y=NULL) +
  guides(color = guide_legend(byrow = TRUE, ncol=1)) + 
  
  theme_bw() +
  theme(text = element_text(size = 16, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.5,0.1, 0.5), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),

        #axis.text.x = element_text(angle = 45, vjust=1, hjust=1),

        strip.background = element_blank(),
        strip.placement = "outside",

        legend.position = c(0.8,0.8),
        legend.key.spacing.y = unit(0, 'mm'), 
        legend.background = element_rect(fill="transparent"),
        #legend.position = "right",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm")) 

fig1

```

## Spectram analysis - Y

```{r fig1-y}
y_spec <- spectrum_df(y)

y_mat <- cbind(y_eq, y_wa, y_snr)
x_spec <- sapply(1:p, function(i) spectrum_df(y_mat[,i], span=1)$Spec)

df_spec <- data.frame(Freq=y_spec$Frequency, 
                        y=y_spec$SpectralDensity, 
                        x_spec) %>% 
  gather(Group,Spec,2:5)

df_spec$Group <- factor(df_spec$Group)
summary(df_spec)

df_spec$Group <- factor(df_spec$Group, levels = c("y","X1","X2", "X3"))
fig1.d <- ggplot(df_spec) +

  geom_line(aes(Freq, Spec, color=Group),linewidth=1) +

  scale_y_log10("Spectrum", limits=c(10e-5,10e3),
                breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +

  scale_color_manual(values=c("black", "red","blue","green"), labels=expression(y[Truth], y[Equal],y[WA],y[SNR])) + 
  labs(x="Frequency", y=NULL) +
  guides(color = guide_legend(byrow = TRUE, ncol=1)) + 
  
  theme_bw() +
  theme(text = element_text(size = 16, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.5,0.1, 0.5), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),

        #axis.text.x = element_text(angle = 45, vjust=1, hjust=1),

        strip.background = element_blank(),
        strip.placement = "outside",

        legend.position = c(0.8,0.8),
        legend.key.spacing.y = unit(0, 'mm'), 
        legend.background = element_rect(fill="transparent"),
        #legend.position = "right",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm")) 

fig1.d

```


## Figure 1
```{r plt1}

plt1 <- cowplot::plot_grid(fig,fig1,fig1.c,fig1.d, ncol=2, labels=LETTERS, 
						               label_size=12,
                           label_fontfamily = "serif",
                           label_fontface = "bold",
                           label_colour = "black")


plt1

## save plot 
ggsave(paste0("Figure1_",model,".jpg"), plt1, width = 9, height = 7,  dpi=500)
```

# Frequency based SNR optimization

It is equivalent to MISO Wiener filtering

```{r freq-snr}
wf <- "d4"
if(wf!="haar") v <- as.integer(parse_number(wf)/2) else v <- 1
J <- floor(log2(n/2)) - 1
J <- 6
mode <- 'DWT'; pad="zero"; boundary="periodic"

y_snr_freq <- SNRopt_freq(y, x, mode, wf, J, pad, boundary, option="Truth")$merged

summary(y_snr_freq)

cor(y,cbind(y_eq, y_wa, y_snr, y_snr_freq))

flag.mode <- switch(1, "Truth", "Est")
if(flag.mode =="Truth"){

  y_wa_ls <- sapply(1:n_ensemble, function(i) df_mat[[i]]$x%*%WA(cov(df_mat[[i]]$e)))
  
  y_snr_ls <- sapply(1:n_ensemble, function(i) df_mat[[i]]$x%*%SNRopt(df_mat[[i]]$N,df_mat[[i]]$a))
  
  y_snr_freq_ls <- sapply(1:n_ensemble, function(i) SNRopt_freq(df_mat[[i]]$y,df_mat[[i]]$x, mode, wf, J, pad, boundary, option="Truth")$merged)
} else {
  y_wa_ls <- sapply(1:n_ensemble, function(i) WA_est(x=df_mat[[i]]$x)$merged)
  
  y_snr_ls <- sapply(1:n_ensemble, function(i) SNRopt_est(df_mat[[i]]$y, df_mat[[i]]$x)$merged)
  
  y_snr_freq_ls <- sapply(1:n_ensemble, function(i) SNRopt_freq(df_mat[[i]]$y,df_mat[[i]]$x, mode, wf, J, pad, boundary, option="Est", scale_factor = F)$merged)
}


```

## Merged products in frequency

```{r merge2}

df_y <- data.frame(No=1:n, y, y_wa, y_snr,y_snr_freq) %>% gather(Group, value,2:5)
summary(df_y)

my_labeller <- as_labeller(c(y="y [Truth]", 
                             y_wa="y [WA]", 
                             y_snr="y [SNR]", 
                             y_snr_freq="y [SNR(w)]"), 
							 default = label_parsed)

df_y$Group <- factor(df_y$Group, levels = c("y","y_wa", "y_snr", "y_snr_freq"))

p2.1 <- ggplot(df_y) + 
  geom_line(aes(x=No, y=value, color=Group), linewidth=1) + 

  facet_wrap(Group~., strip.position="left", ncol = 1, scale="fixed", labeller = my_labeller) + 
  labs(x=NULL, y=NULL) + 
  #scale_color_manual(values=col_qual) + 
  scale_color_manual(values=c("black","red","blue","green")) + 
  
  theme_bw() +
  theme(text = element_text(size = 20, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.1,0.1, 0.1), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.border = element_blank(), 
        
        panel.spacing = unit(0, "lines"), 
        strip.placement = "outside", 
        strip.background = element_blank(), 
        strip.text.y.left = element_text(angle = 0), 

        #axis.title.x = element_text(angle = 0), 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),

        legend.position = "none",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm"))

p2.1

```


## Spectrum comparsion - merged

```{r spec}

if(FALSE){
y_spec1_r <- sapply(1:n_ensemble, function(i) spectrum_df(df_mat[[i]]$y)$Spect) %>% rowMeans()

y_wa_r <- sapply(1:n_ensemble, function(i) spectrum_df(y_wa_ls[,i])$Spect) %>% rowMeans()

y_spec2_r <- sapply(1:n_ensemble, function(i) spectrum_df(y_snr_ls[,i])$Spect) %>% rowMeans()

y_spec3_r <- sapply(1:n_ensemble, function(i) spectrum_df(y_snr_freq_ls[,i])$Spect) %>% rowMeans()
} else {

  y_wa_r <- spectrum_df(y_wa, span=1)$Spect
  
  y_spec2_r <- spectrum_df(y_snr, span=1)$Spect
  
  
  y_spec3_r <- spectrum_df(y_snr_freq, span=1)$Spect
}

df_y_spec <- data.frame(Freq=y_spec$Frequency, 
                        y=y_spec$SpectralDensity, 
                        y_wa=y_wa_r,
                        y_snr=y_spec2_r,
                        y_snr_freq=y_spec3_r) %>% 
  gather(Group,Spec,2:5)

df_y_spec$Group <- factor(df_y_spec$Group)
summary(df_y_spec)
df_y_spec$Group <- factor(df_y_spec$Group, levels = c("y","y_wa", "y_snr", "y_snr_freq"))


p2.2 <- ggplot(df_y_spec) +

  geom_line(aes(Freq, Spec, color=Group),linewidth=1) +

  scale_y_log10("Spectrum", limits=c(10e-5,10e3),
                breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x))) +

  labs(x="Frequency", y=NULL) +
  scale_color_manual(values=c("black","red","blue","green"), labels=expression(y[Truth],y[WA],y[SNR],y[SNR(w)])) + 

  theme_bw() +
  theme(text = element_text(size = 16, family="serif", face="bold"),
        plot.margin = unit(c(0.5,0.5,0.1, 0.5), "cm"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),

        #axis.text.x = element_text(angle = 45, vjust=1, hjust=1),

        strip.background = element_blank(),
        strip.placement = "outside",

        legend.position = c(0.8,0.8),
        legend.key.spacing.y = unit(0, 'cm'), 
        legend.background = element_rect(fill="transparent"),
        #legend.position = "right",
        legend.title=element_blank(),
        legend.key.width = unit(1,"cm"))

p2.2

```

## Metric comparison

```{r met}
# MSE 
summary(y_wa_ls)

MSE_wa <- sapply(1:n_ensemble, function(i) mean((y_wa_ls[,i]-df_mat[[i]]$y)^2))
MSE_snr <- sapply(1:n_ensemble, function(i) mean((y_snr_ls[,i]-df_mat[[i]]$y)^2))
MSE_snr_freq <- sapply(1:n_ensemble, function(i) mean((y_snr_freq_ls[,i]-df_mat[[i]]$y)^2))

# Correlation
R_wa <- sapply(1:n_ensemble, function(i) cor(y_wa_ls[,i],df_mat[[i]]$y)^2)
R_snr <- sapply(1:n_ensemble, function(i) cor(y_snr_ls[,i],df_mat[[i]]$y)^2)
R_snr_freq <- sapply(1:n_ensemble, function(i) cor(y_snr_freq_ls[,i],df_mat[[i]]$y)^2)

df_metric <- cbind(Group="MSE", data.frame(X1=MSE_wa, X2=MSE_snr, X3=MSE_snr_freq)) %>% 
  rbind(cbind(Group="R2",data.frame(X1=R_wa, X2=R_snr, X3=R_snr_freq))) %>% 
  gather(Model, value, 2:4)

df_metric$Model <- factor(df_metric$Model, labels=expression(WA,SNR,SNR(w)))
summary(df_metric)

p2.3 <- ggplot(df_metric %>% subset(Group=="R2"), aes(x=Model, y=value, fill=Model)) + 
  
    geom_boxplot(outliers = F) +
      stat_summary(fun=mean, geom="point", position=position_dodge(0.75), 
               shape=24, size=1, color="red") +
  
    labs(y=expression(R^2), x=NULL) + 
    scale_y_continuous(limits = c(0,1.25)) + 
  
    theme_bw() +
    theme(text = element_text(size = 16, family="serif", face="bold"),
          plot.margin = unit(c(0.5,0.5,0.1, 0.5), "cm"),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
  
          #axis.text.x = element_text(angle = 45, vjust=1, hjust=1),
  
           legend.position = c(0.8,0.8),
          legend.key.spacing.y = unit(0.1, 'cm'), 
          legend.background = element_rect(fill="transparent"),
          #legend.position = "right",
          legend.title=element_blank(),
          legend.key.width = unit(1,"cm"))


p2.3


p2.4 <- ggplot(df_metric %>% subset(Group=="MSE"), aes(x=Model, y=value, fill=Model)) + 
  
    geom_boxplot(outliers = F) +
    stat_summary(fun=mean, geom="point", position=position_dodge(0.75), 
               shape=24, size=1, color="red") +
  
    labs(y=expression(MSE), x=NULL) + 
    scale_y_continuous(limits = c(0,1.2)) + 
    #scale_fill_manual(values=viridis(3)) + 
  
    theme_bw() +
    theme(text = element_text(size = 16, family="serif", face="bold"),
          plot.margin = unit(c(0.5,0.5,0.1, 0.5), "cm"),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
  
          #axis.text.x = element_text(angle = 45, vjust=1, hjust=1),
  
          legend.position = c(0.8,0.8),
          legend.key.spacing.y = unit(0.1, 'cm'), 
          legend.background = element_rect(fill="transparent"),
          #legend.position = "right",
          legend.title=element_blank(),
          legend.key.width = unit(1,"cm"))


p2.4

```


## Figure 2
```{r plt2}

plt2 <- cowplot::plot_grid(p2.1,p2.2, p2.3, p2.4, ncol=2, labels=LETTERS, 
						               label_size=12,
                           label_fontfamily = "serif",
                           label_fontface = "bold",
                           label_colour = "black")

plt2

## save plot 
ggsave(paste0("Figure2_",model,"_",flag.mode,"_scaleF.jpg"), plt2, width = 9, height = 9,  dpi=500)
```


